Model Checking Differentially Private Properties

### 2018-01-27 examples.tex
add background info about the "threshold" algorithm

\paragraph{Online Model.}
Below we describe an online model adapted from \cite{}: it .....

>>>>

\paragraph{Online Model.}
Below we describe an online model adapted from \cite{}: it is used in the scenario where a large amount of queries occur, but we only care for the queries which 
are above a given threshold. Other queries below the threshold are considered "irrelevent" and might be discarded. In \cite{}, since the model is set for continuous database, the Laplace mechanism is applied to both queries and the threshold. In our model, the database is discrete and instead the geometric mechanism is applied.
